An exploratory analysis of the influence of resource use on the yield verse quality trade-off in Australian vineyards

### 2023-07-28 article.tex
Added scatter plot figures to model comparison

% wHY ARE WE COMPARING MODELS?
% We compare models to see which predictors contributed relatively to each of the models.
%
%Models were compared using $R^2$ values. The comparison of models performance showed that the average price per tonne of grapes describes a great deal of the relationship between predictor and response when comparing Model 2 to Model 4 
% Graph of productivity verse value.
%(see Table \ref*{tab:modelperformance}). 
% This is important but you do not illustrate why
%
% This section needs to be heavily revised. Why are there tails on the distributions? What does a heavy tail indicate?
% What does it look like with respect to disaster events?
% split the discussion sections out of the results!! Even the questions I am asking are answered in the discussion, however they need to be highlighted as aspects of the models here beforehand.
 Reviewing the data to uncover reasons for this included the use of binary variables such as the utilisation of renewable energy, contractors, and the occurrence of disease, fire and frost; however none of these variables were able to explain why some vineyards produced less, or why other vineyards sold at higher prices than predicted. A wide variety of these influences were likely already explained within the use of year and GI Region, or the interaction of both variables. The change between some regions was dramatic, with particularly warmer and drier regions producing much higher volumes of grapes at lower prices (See Figures 5 and 6). The use of other variables and methods, specifically splines, were able to create a more normally distributed set of residuals but at a drastically reduced accuracy when comparing R2 and RSE. The introduction of known average prices per tonne also helped increase R2 values a small amount; it is important to not that it is common practice for wineries to purchase grapes at a regional average rate, likely resulting in much less variance within a region.

>>>>

\begin{figure}\label{fig:yield_vs_value}
  \includegraphics{yield_verse_value.pdf}}
  \caption{Scatter plot of vineyard yield against the product of yield and average price per tonne. The axes are in standard deviations with points coloured by climate.}
\begin{figure}\label{fig:yield_vs_value_area}
  \includegraphics{yield_verse_value_by_area.pdf}}
    \caption{Scatter plot of vineyard yield against the product of yield and average price per tonne as ratios to area harvested. The axes are in standard deviations with points coloured by climate.}
% wHY ARE WE COMPARING MODELS?
% We compare models to see which predictors contributed relatively to each of the models.
%Models were compared using $R^2$ values. The comparison of models performance showed that the average price per tonne of grapes describes a great deal of the relationship between predictor and response when comparing Model 2 to Model 4 
% Graph of productivity verse value.
%(see Table \ref*{tab:modelperformance}). 
% This is important but you do not illustrate why
% This section needs to be heavily revised. Why are there tails on the distributions? What does a heavy tail indicate?
% What does it look like with respect to disaster events?
% split the discussion sections out of the results!! Even the questions I am asking are answered in the discussion, however they need to be highlighted as aspects of the models here beforehand.
 Reviewing the data to uncover reasons for this included the use of binary variables such as the utilisation of renewable energy, contractors, and the occurrence of disease, fire and frost; however none of these variables were able to explain why some vineyards produced less, or why other vineyards sold at higher prices than predicted. A wide variety of these influences were likely already explained within the use of year and GI Region, or the interaction of both variables. The change between some regions was dramatic, with particularly warmer and drier regions producing much higher volumes of grapes at lower prices (See Figures 5 and 6). The use of other variables and methods, specifically splines, were able to create a more normally distributed set of residuals but at a drastically reduced accuracy when comparing R2 and RSE. The introduction of known average prices per tonne also helped increase R2 values a small amount; it is important to not that it is common practice for wineries to purchase grapes at a regional average rate, likely resulting in much less variance within a region.
